Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-18 paper/paper.tex
pass on transplantation

\begin{figure}[h]
  \centering
  \includegraphics[trim=0 0 0 0,clip,width=0.4\textwidth]{R/stackedbar/stacked}  
  \caption{\label{fig:summary}Summary of results.}
\end{figure}

\subsection{Test Transplantation}
\label{sec:transplantation}
\label{sec:stability}

\Mar{REVISE}We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once a day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that all engines we analyzed, but \chakra{}, use some
variant of the Test262 suite as part of their regression
process\Mar{with fewer tests?}. We used the official version
instead\Mar{, which updates tests regularly?}. To sum, we observed
that \Fix{...} \Mar{justify regressions using the Kangax report}

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \midrule
    \jsc{} & 2278 & - & - & - & - & - & - \\
    \veight{} & 1213 & - & - & - & - & - & - \\
    \chakra{} & 7041 & - & - & - & - & - & - \\
    \smonkey{} & 1761 & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
  \begin{tabular}{crr}
    \toprule
    & \# buckets & avg. \# files per bucket \\
    \midrule
    \radamsa{} & & \\
    \quickfuzz{} & & \\    
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[trim=0 120 0 150,clip,width=0.4\textwidth,scale=0.3]{R/stackedbar/stacked}  
  \caption{\label{fig:summary}Summary of results.}
\end{figure}

\subsection{Test Transplantation}
\label{sec:transplantation}
\label{sec:stability}
\Igor{
  Marcelo, de acordo com os resultados obtidos, prefiro retirar
  esse paragrafo e tabela, nao houve perda/aumento de falhas nesses
  ultimos 7 dias, acho que valeria a pena se fizessemos isso 1 vez por semana
  durante os ultimos meses.
}
\Mar{REVISE}We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once a day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that all engines we analyzed, but \chakra{}, use some
variant of the Test262 suite as part of their regression
process\Mar{with fewer tests?}. We used the official version
instead\Mar{, which updates tests regularly?}. To sum, we observed
that \Fix{...} \Mar{justify regressions using the Kangax report}

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \midrule
    \jsc{} & 2278 & 2278 & 2278 & 2278 & 2278 & 2278 & - \\
    \veight{} & 1213 & 1213 & 1213 & 1213 & 1213 & 1213 & - \\
    \chakra{} & 7041 & 7041 & 7041 & 7041 & 7041 & 7041 & - \\
    \smonkey{} & 1761 & 1761 & 1761 & 1761 & 1761 & 1761 & - \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
  \begin{tabular}{crr}
    \toprule
    & \# buckets & avg. \# files per bucket \\
    \midrule
    \radamsa{} & \Fix{62} & \Fix{1.62 (101/62)}\\
    \quickfuzz{} & & \\    
    \bottomrule     
  \end{tabular}
\end{table}
